# Hydrometry and the Water Balance

This chapter will begin with a brief review of several hydrometry methods suitable in SC from simple to state of the art, and the uncertainties associated with each method. That will be followed by an overview of streamflow data available in the National Water Information System [us_geological_survey_national_2018]. Finally, the water balance concept will be developed and explored at different spatio-temporal scales.

Water Balance
Soil pedon scale, acre scale, field scale, parcel scale, watershed scale, water distribution system service area scale, state wide scale.

'An objective and parsimonious approach for classifying natural flow regimes...' [@archfield_objective_2014]

In this work, $ Q $ will be used to represent volumetric flow rates of water, according to convention in physics and engineering [cite ?]

**Baseflow**
'An automated, web based, hydrograph assessment tool' [@lim_automated_2005]
baseflow in the piedmont. [@wilson_groundwater-baseflow_1974]

review of baseflow techniques [@brodie_review_2005]

** Flow Duration Curves **
[@searcy_flow-duration_1959]

"Flow-duration curves I" [@vogel_flow-duration_1994]

"Time series analysis of hydrologic data for water resources planning and management: a review" [@machiwal_time_2009]

Between 1668 and 1670, Pierre Perrault measured rainfall and streamflow to create a simple water balance for the Seine river basin in France.  He found that the vast majority of the water in that basin came from rainfall, contrary to the previous theory which held that seawater was pulled up through the ground to be recycled as streamflow. [@chapelle_hidden_1997] Baker and Horton provide a different, but similar history. [@baker_historical_1936]



Long time series are really helpful, and short time series can be very misleading. [@feaster_importance_2010]

Low flow estimates and how they can change over time [@feaster_7q10_2010]

USGS has developed an R package called *dataRetrieval* [@R-dataRetrieval] which we can use to download data from their servers. All of the data available within the greater South Carolina drainage area could be relevant for this project.^[A wider area could be considered when looking for reference gages, perhaps including a portion of Delaware.(cite Feaster)] This area includes all of SC, and portions of GA, NC, and VA. It can be approximated using 4 digit HUC codes 0304, 0305, and 0306. At the time of this writing, however, the dataRetrieval package doesn't offer the functionality we need to easily query by HUCs. 

So, first the data from all sites in the four states has been downloaded, then filtered to include only sites within the 3 HUC4's. With a list of HUC8s, it would be possible to batch query the USGS rest service, but that is more difficult to implement.
  
There are many options available with USGS' services. Two of interest cannot be used together - catalog output and expanded output. Catalog output: 
_"...provides detailed period of record information for certain output formats. The period of record indicates date ranges for a certain kind of information about a site, for example the start and end dates for a site's daily mean streamflow."_
  
Expanded output: 
_"...provides a rich set of extended site attributes such as hydrologic unit code, drainage area and site time zone."_ 

*Statistics: uncertainty. It has become a common trope, when confronted with methodological problems in existing models, to respond that the stream gages have xyz amounts of uncertainty. This claim will be reviewed here.*


Both are loaded and reviewed.
  
```{r siteDataDownload, cache=TRUE, eval=EvalOptions$Download}

library(dataRetrieval)
sites_catalog <- bind_rows(
  lapply(c("SC", "NC", "GA", "VA"), function(x) {
    readNWISdata(stateCd = x, service = "site", 
                 seriesCatalogOutput = TRUE) } ) ) %>%
  mutate(huc4 = str_sub(huc_cd, end=4)) %>%
  filter(huc4 %in% c('0304', '0305', '0306'))

dnr_save(sites_catalog, input=TRUE)
# saveInput(sites_catalog, "sites_catalog-40.rds")

sites_expanded <- bind_rows(
  lapply(c("SC", "NC", "GA", "VA"), function(x) {
    readNWISdata(stateCd = x, service = 'site',
                 siteOutput = 'expanded') %>%
      mutate(construction_dt = as.character(construction_dt),
         well_depth_va = as.numeric(well_depth_va),
         hole_depth_va = as.numeric(hole_depth_va) ) } ) ) %>%
  mutate(huc4 = str_sub(huc_cd, end=4)) %>%
  filter(huc4 %in% c('0304', '0305', '0306'))

dnr_save(sites_expanded, input=TRUE)
# saveInput(sites_expanded, "sites_expanded-40.rds")
```


## USGS Monitoring Gages

sites_catalog is much longer than sites_expanded because sites_catalog contains an entry for each statistic of each parameter at each site, whereas sites_expanded contains only one entry per site.

Additional key tables decode certain the columns in these site tables. These key tables are available on the USGS website, and they have been combined into an Excel workbook and subsequently joined to the gage tables. 

An additional table can be aggregated from the sites_catalog table: sites_parameters. This table contains one entry for each parameter measured at each site.

```{r siteCodeDictionaries}
## TODO: decode sites_expanded$instruments_cd
# dnr_load(sites_expanded)
# dnr_load(sites_catalog)

gageSites <- readInput('sites_expanded-40.rds')
gageCatalog <- readInput('sites_catalog-40.rds')

read_dictionary <- function(sheet) {
  read_excel('_input/USGS_code_dictionary.xlsx', sheet=sheet) }

gageCatalog %<>% 
  left_join(read_dictionary(1), by = "stat_cd") %>%
  left_join(read_dictionary(2)[,1:3], by = "parm_cd") %>%
  left_join(read_dictionary(3) %>%
            dplyr::select(site_tp_cd, site_tp_ln), by = "site_tp_cd") %>%
  rename(lat=dec_lat_va, lng=dec_long_va) %>%
  mutate(begin_date = ymd(begin_date, truncated=2),
         end_date = ymd(end_date, truncated=2))

gageParameters <- gageCatalog %>%
  group_by(parameter_group_nm, parameter_nm, site_no) %>%
  summarise(begin_date = min(begin_date),
            end_date = max(end_date)) %>%
  ungroup()

gageSites %<>%
  left_join(read_dictionary(3) %>%
            dplyr::select(site_tp_cd, site_tp_nm, site_tp_ln, site_tp_ds), by = "site_tp_cd") %>%
  left_join(read_dictionary(4), by = c("state_cd", "aqfr_cd")) %>%
  left_join(read_dictionary(5), by = "aqfr_type_cd") %>%
  left_join(read_dictionary(6), by = c("state_cd", "nat_aqfr_cd")) %>%
  left_join(read_dictionary(7), by = "reliability_cd") %>%
  left_join(read_dictionary(8), by = "topo_cd") %>%
  rename(lat=dec_lat_va, lng=dec_long_va) %>%
  mutate(id = paste0(site_no, project_no),
         state_nm = case_when(
           state_cd == "45" ~ "SC",
           state_cd == "13" ~ "GA",
           state_cd == "37" ~ "NC",
           TRUE ~ "VA"))
row.names(gageSites) <- gageSites$id

dnr_save(gageSites); dnr_save(gageParameters); dnr_save(gageCatalog)

# saveTemp(gageSites, "gageSites-41.rds")
# saveTemp(gageParameters, "gageParameters-41.rds")
# saveTemp(gageCatalog, "gageCatalog-41.rds")
```

The monitoring gage sites are classified in to different types. The types of sites available in the greater SC watershed are described in the table below (ordered from most abundant to least):

```{r site_types_summary_table}
dnr_load(gageSites, temp=TRUE)
dnr_load(gageCatalog, temp=TRUE)
dnr_load(gageParameters, temp=TRUE)

# gageSites2 <- readTemp('gages-Export4Dashboard.rds') 
# gageCatalog <- readTemp('gageCatalog-41.rds') 
# gageParameters <- readTemp('gageParameters-41.rds') 

## Run data export for dashboard on the gageSites
# saveRDS(gageSites, "_shinyApps//41-NWIS-AllSitesApp//Sites.rds")
# saveRDS(gageCatalog, "_shinyApps//41-NWIS-AllSitesApp//Catalog.rds")
# # saveRDS(gageParameters, "41-NWIS-AllSitesApp//Parameters.rds")

gageTypeStateSummary <- gageSites %>%
  group_by(site_tp_ln, state_nm, site_tp_ds) %>%
  summarise(Count = n()) %>%
  spread(state_nm, Count, fill=0) %>%
  mutate(Total = SC+GA+NC+VA) %>%
  dplyr::select(`Site Type` = site_tp_ln, SC, NC, GA, VA, Total, 
         `Description` = site_tp_ds) %>%
  arrange(desc(Total))

# saveRDS(gageTypeStateSummary,
#         "_shinyApps//41-NWIS-AllSitesApp//TypeStateSummary.rds")

kable(gageTypeStateSummary[,c(1,7)])

```

Here is a breakdown of the site types by states (sites not within the greater SC watershed are not included). 

```{r NWIS-gageTypeStateSummary-table}
kable(gageTypeStateSummary[,-7])
## Can I make the Description be a pop-up when you hover over Site Type? 

# There are many well and stream sites. They will be examined in greater detail 
# in the following pages. Below is an interactive map of the other site types.
rm(gageTypeStateSummary)
```


Each monitoring site collects or has collected data for one or more parameters. When all of the sites are taken into consideration, there is an impressive variety of parameters. The parameters are listed alphabetically by group in the table below. Why are there so many NAs?
```{r NWIS-parameterGroupSummary}
## Parameter Group Summary
parameterGroups <-
  group_by(gageCatalog, parameter_group_nm) %>%
  summarise(`Parameter Group`=unique(parameter_group_nm),
            Sites=length(unique(site_no)),
            Parameters=# length(unique(parameter_nm)),
              if(length(unique(parameter_nm))==1) {
                unique(parameter_nm) 
                } else {
                  as.character(length(unique(parameter_nm)))},
            Statistics=
              if(length(unique(stat_desc))==1) {
                unique(stat_desc) 
                } else {
                  as.character(length(unique(stat_desc)))},
            Records=n(),
            `Parameter List`=paste(sort(unique(parameter_nm)), 
                                   collapse="; ")) %>%
  ungroup() %>% select(-1)

# saveRDS(parameterGroups, "41-NWIS-AllSitesApp//parameterGroups.rds")

parameters <- select(gageParameters, 1,2) %>% unique()
# saveRDS(parameters, "41-NWIS-AllSitesApp//parameters.rds")

parameterGroupCatalog <- group_by(
  gageParameters, site_no, parameter_group_nm) %>%
  summarise(begin_date = min(begin_date), 
            end_date=max(end_date)) %>% ungroup()

# saveRDS(parameterGroupCatalog, "41-NWIS-AllSitesApp//parameterGroupCatalog.rds")

kable(select(parameterGroups, -`Parameter List`))
```
The complete list of parameters available in the study area is 70 pages long. The physical parameters could be reviewed selectively. 
```{r NWIS-parameterGroupSummaryTable}
# kable(select(parameterGroups, 1,6))
## This prints to some 70 pages...

## TODO: list and describe physical parameters
```

The table below shows the types of statistical values that are available in the catalog, and the number of time series for each type of value. (A time series is composed of one or more recorded observations over time at a given site). Why are there so many NAs?

```{r NWIS-stat-summary}
## Stat summary
statSummary <- group_by(gageCatalog, stat_desc) %>%
  summarise(Records = n()) %>%
  rename(Statistics = stat_desc)

# saveRDS(statSummary, "41-NWIS-AllSitesApp//statSummary.rds")

kable(statSummary)
```


```{r NWIS-cleanup}

## gageSites contains 1620 rows with either missing or 
## invalid lat/lon values and will be ignored
# rename(lat = dec_lat_va, lng = dec_long_va)

rm(# gageSites, gageParameters, gageCatalog, 
  parameterGroups, parameterGroupCatalog, parameters, statSummary)

```





## NWIS Surface Water

TODO: Look at the parameters and date ranges offered by the stream gages.
TODO: Make the Gant chart looking graph with gages and P.O.R.'s

```{r NWIS-SurfaceWater-DateRange}

# gageSites <- readTemp('gageSites-41.rds')
# gageCatalog <- readTemp('gageCatalog-41.rds')
# gageParameters <- readTemp('gageParameters-41.rds')
  
## For the surface water app
surfaceSites <- gageSites %>%
  filter(site_tp_nm %in% c("Stream", "Lake", "Tidal SW", "Estuary", "Spring")) 

## A table summarizing the types of parameters in each state
inner_join(gageParameters, surfaceSites[c("site_no", "state_nm")]) %>%
  group_by(parameter_group_nm, state_nm) %>%
  summarise(Count = n()) %>%
  spread(state_nm, Count, fill=0) %>%
  mutate(Total = SC+GA+NC+VA) %>%
  arrange(desc(Total))
# unique(x$parameter_group_nm)

## A table summarizing the physical parameters in each state
inner_join(gageParameters, surfaceSites[c("site_no", "state_nm")]) %>%
  filter(parameter_group_nm == "Physical") %>%
  group_by(parameter_nm, state_nm) %>%
  summarise(Count = n()) %>%
  spread(state_nm, Count, fill=0) %>%
  mutate(Total = SC+GA+NC) %>%
  arrange(desc(Total)) %>%
  dplyr::select(
    GA, NC, SC, Total,
    `Physical Parameter Measured at Stream, Lake, Tidal, Estuary, or Spring Sites` = parameter_nm)
### Make this a dynamic shiny app?

```



```{r USGS-DownloadSurfaceFlowData, eval=EvalOptions$Download}
surfaceFlowSites <- semi_join(
  surfaceSites, filter(gageCatalog, parm_cd == "00060"), by="site_no")

### Download All Surface Flow Data
for(i in 1:nrow(surfaceFlowSites)) {
  print(i)
  flowData <- readNWISdv(
    siteNumber = surfaceFlowSites$site_no[i],
    parameterCd = '00060') %>% renameNWISColumns()
  
  if(length(flowData) == 0) next
  
  if(!("Flow" %in% names(flowData)) &&
     !("Flow_cd" %in% names(flowData) ) ) {
    flowData %<>% rename(Flow = PUBLISHED_Flow,
                         Flow_cd = PUBLISHED_Flow_cd ) }
  
  flowData %<>% dplyr::select("site_no","Date","Flow","Flow_cd")
  
  if(i == 1) {AllSurfaceFlowData <- flowData
  } else {AllFlowData <- rbind(AllSurfaceFlowData, flowData) } }

AllSurfaceFlowData %<>% dnr_removeNWISattributes() %>%
  unique()

dnr_save(AllSurfaceFlowData, input=TRUE)
# saveInput(AllSurfaceFlowData,"AllSurfaceFlowData.rds")
## TODO: Graph it somehow.
## TODO: The gage data availability chart
```

```{r NWIS-UpdateSurfaceFlowDate, eval=EvalOptions$Update}

## TODO: update provisional data
## TODO: update Sites

AllSurfaceFlowData <- readInput("AllSurfaceFlowData.rds")

library(tidyverse)

surfaceFlowSites <- semi_join(
  surfaceSites, filter(gageCatalog, parm_cd == "00060"), by="site_no")

surfaceFlowSites2 <- inner_join(
  surfaceSites, 
  filter(gageCatalog, parm_cd == "00060") %>% ##  & stat_cd=='00003'
    select(site_no, parameter_nm, stat_name, begin_date, end_date), 
  by="site_no")


print("Downloading new surface flow data")

for(i in 1:nrow(surfaceFlowSites)) {
  flowData <- readNWISdv(
    siteNumber = surfaceFlowSites$site_no[i],
    parameterCd = '00060',
    startDate=max(AllSurfaceFlowData$Date)+1) %>% renameNWISColumns()
  
  if(length(flowData) == 0) next
  
  if(!("Flow" %in% names(flowData)) &&
     !("Flow_cd" %in% names(flowData) ) ) {
    flowData %<>% rename(Flow = PUBLISHED_Flow,
                         Flow_cd = PUBLISHED_Flow_cd ) }
  
  flowData %<>% dplyr::select("site_no","Date","Flow","Flow_cd")
    if(i == 1) {newSurfaceFlowData <- flowData
  } else {newSurfaceFlowData <- rbind(newSurfaceFlowData, flowData) } }

newSurfaceFlowData %<>% dnr_removeNWISattributes() %>%
  unique()

# nrow(filter(newSurfaceFlowData, Date==today()-2))

AllSurfaceFlowData <- rbind(AllSurfaceFlowData, newSurfaceFlowData)
rm(newSurfaceFlowData, flowData)
dnr_save(AllSurfaceFlowData, temp=TRUE)

usethis::use_data(AllSurfaceFlowData)
# usethis::use_data(gageCatalog)
# usethis::use_data(surfaceSites)
usethis::use_data(surfaceFlowSites)



x <- select(surfaceFlowSites2, station_nm, site_no, lat, lng, 
       state_nm, site_tp_ln, parameter_nm, stat_name, 
       begin_date, end_date) %>%
  filter(site_tp_ln %in% c("Stream", "Tidal stream") & 
           stat_name=="MEAN") %>%
  mutate(Length_Days = end_date-begin_date) 

x2 <- x[duplicated(x$site_no),] %>%
  select(site_no, begin_date, end_date, Length_Days)

x3 <- left_join(x[!duplicated(x$site_no),], x2, by='site_no',
                suffix=c('.1', '.2'))

y <- filter(AllSurfaceFlowData, !is.na(Flow)) %>%
  group_by(site_no, Flow_cd) %>%
  summarise(days=n()) %>%
  spread(Flow_cd, days, fill=0) %>%
  ungroup()


library(xlsx)
left_join(x3, y) %>%
  write.xlsx("Mean Daily Stream Discharge Length of Records.xlsx")




getwd()

```


```{r NWIS-SurfaceWater-Reports, eval=FALSE }
# dnr_load(AllSurfaceFlowData)

abbrev <- function(str, pat, rep) {
  str_replace_all(str, regex(pat, ignore_case=TRUE), rep) }

reduceGageStationNames <- function(stationNames) {
  stationNames %>%
    abbrev('SAVANNAH RIVER SITE', 'SRS') %>%
    
    abbrev('  ', ' ') %>% abbrev(',SC', '') %>%
    abbrev(',S.C.', '') %>% abbrev(', S.C.', '') %>%    
    abbrev(', S. C.', '') %>% abbrev(' S C', '') %>% 
    abbrev(' S. C.', '') %>% abbrev(", SC", '') %>%
    abbrev(',GA', '') %>% abbrev(', GA', '') %>%
    abbrev(',NC', '') %>% abbrev(', NC', '') %>%
    
    abbrev('SOUTH ', 'S.') %>% abbrev('NORTH ', 'N.') %>%
    abbrev('EAST', 'E.') %>% abbrev('WEST', 'W.') %>%
    abbrev('LITTLE', 'Lil') %>% abbrev('BIG', 'Bg') %>%
    abbrev('UPPER', 'Upr') %>% abbrev('MIDDLE', 'Mdl') %>% 
    abbrev('LOWER', 'Lwr') %>%
    abbrev("NEAR", "nr") %>% abbrev(" AT ", ' @ ') %>% 
    abbrev('ABOVE', 'Abv') %>% abbrev('BELOW', 'Blw') %>% 
    
    abbrev("CREEK", "Crk") %>% abbrev("RIVER", "Rvr") %>%
    abbrev('CANAL', 'Cnl') %>% abbrev('FORD', 'Frd') %>%
    abbrev('FORK', 'Frk') %>% abbrev('BRANCH', 'Bnch') %>% 
    abbrev('MOUNT', 'Mt') %>% abbrev('HILL', 'Hl') %>%
    abbrev('BEAVER', 'Bvr') %>% abbrev('TURKEY', 'Trky') %>%
    abbrev('HEADWATER', 'Hdwtr') %>% abbrev('MOUTH', 'Mth') %>%
    abbrev('BEACH', 'Bch') %>% abbrev('PORT', 'Prt') %>%
    abbrev('SWAMP', 'Swmp') %>% abbrev('SHOALS', 'Shls') %>%
    abbrev('TRIBUTARY', 'Trib') %>%
    abbrev(' SPRINGS', 'Spr') %>% abbrev(' SPRING', 'Spr') %>%
    abbrev('ROCKY', 'Rcky') %>% abbrev('ROCK', 'Rck') %>%
    abbrev('GROVE', 'Grv') %>% abbrev('FOREST', 'Frst') %>%
    abbrev('HICKORY', 'Hckry') %>% abbrev('CORNER', 'Crnr') %>%  
    abbrev('LAKE', 'Lk') %>% abbrev('RESERVOIR', 'Res.') %>%
    abbrev('FALLS', 'Fls') %>% abbrev('ISLAND', 'Is.') %>%
    abbrev('AVENUE', 'Ave') %>% abbrev(' ROAD', ' Rd') %>%
    abbrev('RAILROAD', 'RlRd') %>% abbrev('HIGHWAY', 'Hwy') %>%
    abbrev('BOULEVARD', 'Blvd') %>% abbrev('TRAIL', 'Trl') %>%
    abbrev('CROSSROADS', 'CrsRd') %>% abbrev('CROSSROAD', 'CrsRd') %>%
    abbrev('BRIDGE', 'Brdg') %>% abbrev('DAM', 'Dm') %>% abbrev('TAILRACE', 'Tlrc') %>%
    abbrev('FORT', 'Frt') %>% abbrev('VILLE', 'vl') %>%  abbrev('BURG', 'Brg') %>%
    abbrev('MILLS', 'Mls') %>% abbrev('MILL', 'Ml') %>%
    abbrev('PARK', 'Prk') %>%
    
    abbrev('FIRST', '1st') %>% abbrev('SECOND', '2nd') %>%    
    abbrev('NINETYSIX', '96') %>% abbrev('NINETYNINE', '99') %>% abbrev('TWENTY', '20') %>%
    abbrev('EIGHTEEN', '18') %>% abbrev('TWELVE', '12') %>% abbrev('SIX', '6') %>%
    abbrev('FOUR', '4') %>%  abbrev('THREE', '3') %>%
       
    abbrev('MILE ', 'mi') %>% abbrev('GOLF COURSE', 'Golf') %>%
    abbrev('LANDING', 'Lndng') %>% abbrev('POWERHOUSE', 'Pwrhs') %>%
    abbrev('TREATMENT', 'Treat.') %>% abbrev(' PLANT ', ' Plnt') %>%
    abbrev('MEDICAL', 'Med.') %>% abbrev('CENTER', 'Cntr') %>%
    
    abbrev('PEE DEE', 'P.D.') %>% abbrev('YADKIN', 'Yadkn') %>%
    abbrev('SAVANNAH', 'Sav.') %>% abbrev('SITE NO. ', 'Site') %>%
    abbrev('WINSTON-SALEM', 'Winst-Sal') %>% abbrev('ATLANTIC', 'Atlc') %>%
    abbrev('CHARLOTTE', 'Charlt') %>% abbrev('COLUMBIA', 'Cola.')
} # BROAD CATAWBA  WACCAMAW POCOTALIGO COOSAWHATCHIE 

# surfaceSites$station_nm2 <- reduceGageStationNames(surfaceSites$station_nm)
# 
# surfaceSites %>%
#   dplyr::select(station_nm2, station_nm) %>%
#   mutate(name_length = str_length(station_nm),
#          name_length2 = str_length(station_nm2)) %>%
#   arrange(desc(name_length2)) -> y
# head(y, n=25L)
# qplot(y$name_length) ; qplot(y$name_length2)
# rm(y)

surfaceSites$station_nm <- reduceGageStationNames(surfaceSites$station_nm)
surfaceSites$station_nm <- tools::toTitleCase(surfaceSites$station_nm)

dnr_save(surfaceSites, input=TRUE)

```

```{r NWIS-surface-water-cleanup}
rm(gageSites, gageParameters, gageCatalog)

```

```{r NWIS-multi-dimensional-table}
AllSurfaceFlowData <- readInput("AllSurfaceFlowData.rds")

flow <- mutate(AllSurfaceFlowData,
               `Water Year` = year(Date) + ifelse(month(Date)>9,1,0)) %>%
  select(Site=site_no, `Water Year`, Flow)

# flow %>% group_by(site_no) %>%
#   do({mutate(., percentile=rank(Flow)/nrow(.))})
# flow %<>% mutate(yday = yday(Date))
# flow %<>% ungroup()

flow2 <- group_by(flow, Site) %>%
  do({movingAverages(., "Flow", 2:30) %>%
      rename(Flow1=Flow) %>%
      gather("Duration", Flow, Flow1:Flow30) %>%
      mutate(Duration = as.numeric(str_sub(Duration, 5) ) ) %>%
      group_by(Duration, `Water Year`) %>%
      summarise(High = max(Flow, na.rm=TRUE),
                Low = min(Flow, na.rm=TRUE) ) %>%
      ungroup() %>%
      gather("Type", Flow, High, Low) %>%
      group_by(Duration, Type) %>%
      do({mutate(., `Return Interval` = (nrow(.)+1)/
                   ifelse(Type=='High', rank(-Flow), rank(Flow)))})
    } ) %>% ungroup()

flow2 %<>% mutate(`Exceedance Probability`=1/`Return Interval`)

surfaceSites <- readInput("surfaceSites-42.rds") %>%
  select(site_no, `Site Name`=station_nm, `Drainage Area (sqmi)` = drain_area_va)

filter(flow2, Site %in% c("02109500", "02173000", "02196000", "02167582")) %>%
         left_join(surfaceSites, by=c("Site"="site_no")) %>%
  mutate(`CFS/sqmi` = Flow / `Drainage Area (sqmi)`) %>%
  ggplot(aes(group=interaction(Duration, Type),
             # y=Flow,
    y=`CFS/sqmi`, 
    # color=Type, 
    # x=`Return Interval`, 
    color=Duration, 
    x=`Exceedance Probability`)) +
  geom_line() +
  scale_color_gradient(low="red", high="blue") +
  scale_y_log10() + 
  # scale_x_log10() +
  facet_wrap(~`Site Name`, 2 #, scales="free_y"
             )
## TODO: plot mean and median horizontal lines.
  
filter(flow2, Site %in% c("02109500", "02173000", "02196000", "02167582")) %>%
         left_join(surfaceSites, by=c("Site"="site_no")) %>%
  mutate(`CFS/sqmi` = Flow / `Drainage Area (sqmi)`) %>%
  ggplot(aes(# group=interaction(Duration, Type),
             # y=Flow,
    y=`CFS/sqmi`, 
    # color=Type, 
    # x=`Return Interval`, 
    color=`Exceedance Probability`,
    x=Duration)) +
  geom_point() +
  scale_color_gradient(low="red", high="blue") +
  scale_y_log10() + 
  # scale_x_log10() +
  facet_wrap(~`Site Name`, 2 #, scales="free_y"
             )

rm(surfaceSites)
```

```{r NWIS-map}
## Leaflet map with HUC4s, States, nonWellAndStreamSites
## catalog stats for each site.

## site table, map, stat table, 
## when a site is selected, filter map and stat table
## when an area or site is selected in the map, filter tables
## when a stat is selected, filter sites and map.

## ggiraph?

### ToDo: Visualize and explore the two sites tables.
### ToDo: try to find data quality codes.
### ToDo: filter out data that isn't relevant to the app.

```

